MLExplain

### 2018-07-25 paper.tex
Add reference to JSExplain in the abstract

\begin{abstract}
  MLExplain is a step-by-step interpreter for OCaml that enables the
  user to inspect both their program's state and the interpreter's state
  itself. This interpreter aims to provide the user with a better understanding
  of the semantics of OCaml.
\end{abstract}

>>>>

\begin{abstract}
  MLExplain is a step-by-step interpreter for OCaml that enables the
  user to inspect both their program's state and the interpreter's state
  itself. This interpreter is derived from JExplain, a step-by-step interpreter
  for JavaScript. Its original goal is to prove that JSExplain can easily be
  reused with another language. MLExplain also aims to provide the user with a
  better understanding of the semantics of OCaml.
\end{abstract}
